Playing multiple games using deep reinforcement learning, or Spatial Attention network can play (beat) simultaneously multiple games in reinforcement learning

### 2019-09-15 multi_dqn_paper/paper.tex
updated results

{\bf DenseNet network architecture}:
Next tested architecture is DenseNet \cite{bib:densenet_net}. We used four dense blocks. Each dense block consist of four 3x3x32 convolutional layers, one 1x1x32 layer and 2x2 pooling layer.
The main idea is to use state of the art network, which have much bigger capacity and probaly can outperform basic DQN. The main problem can be a lot
of parameters of this network. Thanks dense connection, the much deeper architecture can be used, and much more complex features can be extracted.

{\bf Spatial Attention CNN network architecture}:
The last architecture we tested is Spatial Attention CNN, inspired by \cite{bib:cbam}.
The main idea of attention in CNN is to "amplify" some selected featured and present them to next layer.
Our presented attention module is illustrated on figure \ref{img:spatial_attention_module}.
Input tensor with dimensions $width \times height \times depth$ is processed in convolution block (with kernel size $3 \times 3 \times depth$).
Instead of input features-depth pooling - which is useful in classification attention networks, we are using full features inputs into convolution module (layer).
After convolution the sigmoid non-linear activation is applied on feature maps. Next block is gating unit, which is using point-wise (Hadamard) product.
The last step is addition block, which adds original input and attention features - this can be intepreted as ResNet idea. Full network architectures can be seen in table \ref{tab:networks}.
The formal definition can be written in following term

>>>>

{\bf DenseNet network architecture}:
Next tested architecture is DenseNet \cite{bib:densenet_net}, multi\_net\_1. We used four dense blocks. Each dense block consist of four 3x3x32 convolutional layers, one 1x1x32 layer and 2x2 pooling layer.
The main idea is to use state of the art network, which have much bigger capacity and probaly can outperform basic DQN. The main problem can be a lot
of parameters of this network. Thanks dense connection, the much deeper architecture can be used, and much more complex features can be extracted.

{\bf Spatial Attention CNN network architecture}:
The last architecture we tested is Spatial Attention CNN, inspired by \cite{bib:cbam}, multi\_net\_1.
The main idea of attention in CNN is to "amplify" some selected featured and present them to next layer.
Our presented attention module is illustrated on figure \ref{img:spatial_attention_module}.
Input tensor with dimensions $width \times height \times depth$ is processed in convolution block (with kernel size $3 \times 3 \times depth$).
Instead of input features-depth pooling - which is useful in classification attention networks, we are using full features inputs into convolution module (layer).
After convolution the sigmoid non-linear activation is applied on feature maps. Next block is gating unit, which is using point-wise (Hadamard) product.
The last step is addition block, which adds original input and attention features - this can be intepreted as ResNet idea. Full network architectures can be seen in table \ref{tab:networks}.
The formal definition can be written in following term
